### 2017-11-02 manuscript.rmd
phylobarplot ocde in manuscript

>>>>

###Depth phylo-barplot
```{r, bathy_barplot, echo=F, message=F, warning=F}
d <- lapply(runif(27, 0, 20), rnorm, n=100) #Depth_data_VARS to substitute
ylim <- range(unlist(d))
bx <- lapply(d, function(y) {
  dd <- data.frame(y=y)
  ggplot(dd, aes(x=1, y=y))+geom_boxplot() + ylim(ylim) + theme_inset()
})
names(bx) <- 1:length(ultratree$tip.label)
bx2 <- lapply(bx, function(g) g)
p <- ggtree(ultratree) + geom_tiplab()
HJ <- (-1*p$data$x[1:length(p$data$x)])-1
inset(p, bx2, width=3, height=.03, hjust= HJ) + xlim(0, 4) + coord_flip()
```
